---
title: "Plotly Demo"
author: Felipe Frazatto
date: "September 16, 2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Objective

This presentation will use the `mtcars` data set to draw a graph with `ggplot`
and a simple regression line and convert it to an interactive map with `plotly`.

The idea is to show how easily one can convert a static graph to an interactive 
one with `plotly` just by using the `ggplotly()` function.

## Libraries

```{r echo=TRUE, results='hide', message=FALSE}

library(plotly)
library(ggplot2)

```

## Code for the Graphs (1/3)

The graphs will be displayed on the next slides.


```{r echo=TRUE}

# Labels

gTitle = "Weight Influence on Fuel Economy"
xTitle = "Weight [1000 lbs]"
yTitle = "Miles per Gallon"

```
## Code for the Graphs (2/3)

```{r echo=TRUE}

# Generate ggplot graph
gg <- ggplot(data = mtcars, aes(x = wt, y = mpg)) + 
     geom_point() + 
     geom_smooth(formula = y ~ x, method = "lm") +
     labs(x = xTitle,
          y = yTitle,
          title = gTitle)

# Convert previous plot to plotly
gpc <- ggplotly(gg)

```

## Code for the Graphs (3/3)

```{r echo=TRUE}

# Generate plotly graph
fit <- lm(mpg ~ wt, data = mtcars)

gp <- plot_ly(data = mtcars, y = mpg, x = ~wt) %>% 
     add_markers(y = ~mpg) %>% 
     add_lines(x = ~wt, y = fitted(fit)) %>%
     layout(title = gTitle,
            scene = list(
                 xaxis = list(title = xTitle),
                 yaxis = list(title = yTitle)
                 )
     )

```


## Non Interactive plot with ggplot2

```{r echo=TRUE}
## ggplot
gg

```


## Interactive plot with plotly

```{r echo=TRUE, message=FALSE, warning=FALSE}
# plotly
gp

```


## Converted Plot: ggplot -> plotly

```{r echo=TRUE}
# plotly converted
gpc

```    


## Conclusion

* Both graphs are practically the same (aside from the interactive);
* Easily switch between `ggplot` and `plotly`;
* High quality images.

If you don't know how to use `plotly` very well, you can safely use `ggplot` and
convert the result with `ggplotly`.

## That's all Folks

Thanks